Facility and Time Step Discretization Effects in Fuel Cycle Simulation

### 2015-09-18 paper.tex
add caption to pu comparison fig

\begin{figure*}[!h]
    \centering
    \includegraphics[width=1.0\textwidth]{exp2/puinv.eps}
    \caption[Pu inventory and flow]{
        Pu inventory and flows for all four cases.  In-flows for cases 1 and 3
        are omitted because they are very noisy and obscure useful other
        information.  Larger time steps results in larger per time step
        material flows. These larger flows mean more material is not available
        for supplying to requesters.  This information lag causes more supply
        constraints than occur with smaller time steps - illustrating the
        \emph{inventory drawdown effect}.
    }
    \label{fig:puinv}
\end{figure*}

@@

\begin{figure*}[!h]
    \centering
    \includegraphics[width=0.8\textwidth]{exp2/puinv-compare.eps}
    \caption[TODO]{
        TODO
    }
    \label{fig:puinv-compare}
\end{figure*}

>>>>

\begin{figure*}[!h]
    \centering
    \includegraphics[width=1.0\textwidth]{exp2/puinv.eps}
    \caption[Separated Pu inventory and flow]{
        Separated Pu inventory and flows for all four cases.  In-flows for
        cases 1 and 3 are omitted because they are very noisy and obscure
        useful other information.  Larger time steps results in larger per
        time step material flows. These larger flows mean more material is not
        available for supplying to requesters.  This information lag causes
        more supply constraints than occur with smaller time steps -
        illustrating the \emph{inventory drawdown effect}.
    }
    \label{fig:puinv}
\end{figure*}

@@

\begin{figure*}[!h]
    \centering
    \includegraphics[width=0.8\textwidth]{exp2/puinv-compare.eps}
    \caption{
        Separated Pu inventories for all four cases.  Differences in modeling
        choices are not particularly significant until about year 100 when
        fuel shortages begin.  These differences gradually decay away starting
        in year 140 after the fuel shortages have ebbed.  Higher aggregate Pu
        inventory  during the shortage is correlated with a longer during and
        post shortage recovery period.
    }
    \label{fig:puinv-compare}
\end{figure*}
